---
title: "Pokemon BMI (Q1 2019)"
subtitle: "(Un)official Statistics"
author: "Matt Dray"
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
filter_n <- 20

library("tidyverse")
library("knitr")
library("tools")
library("Rokemon")

pkmn <- read_csv(file = "data/pogo.csv") %>% 
  mutate(bmi = weight_kg/(height_m^2)) %>% 
  group_by(species) %>%
  summarise(count = n(), mean_bmi = mean(bmi)) %>%
  arrange(desc(mean_bmi)) %>% 
  filter(count > filter_n)
```

![Me playing Pokemon Go ([via Giphy](https://giphy.com/gifs/pokemon-pokemongo-lookhuman-l0MYyWeUGYVl5iA8w))](https://media.giphy.com/media/l0MYyWeUGYVl5iA8w/giphy.gif){width=200}

# Very important table

This is some text written in R Markdown to demonstrate the power of writing a script that can be re-run in future to reproduce an output document.

This table shows the mean body mass index (BMI) for Pokemon that appear over `r filter_n` times in the dataset.

```{r table, echo=FALSE}
pkmn %>% 
  mutate(
    species = toTitleCase(species),
    mean_bmi = round(mean_bmi, 1)
  ) %>% 
  rename(Species = species, Count = count, `Mean BMI` = mean_bmi) %>%
  kable()
```

# Very important plot

Good grief, this plot truly tells a very exciting story. I cannot belive my eyes.

```{r plot, echo=FALSE}
pkmn %>%
  filter(count > filter_n) %>%
  gghealth("species", "mean_bmi") +
  labs(
    x = "", y = "BMI",
    title = "Pokemon BMI",
    subtitle = "How is this a thing?",
    caption = "Credit: The Pokemon Company/Niantic"
  )
```
